\thetitle

### 2013-04-17 tfpie/tfpie.tex
Some crap on dispatch.

The structure of this data definition is analagous to the approach of
the previous semester but this example brings to light an important
difference with the functional approach.

>>>>

The structure of this data definition is analagous to the approach of
the previous semester but this example brings to light an important
difference with the functional approach.  The method for computing the
length of the empty list is defined in the {\tt empty\%} class, while
the method for computing the length of a non-empty list is in the {\tt
  cons\%} class.  When a list object is sent the {\tt len} method,
there is no function with a conditional to determine whether the
object is empty or not---instead, the object itself takes care of
computing length based on the {\tt len} method it contains.  This
shift in perspective is at the core of object-orientation: objects
contain their own behavior and the case analysis previously done in
functions is replaced by dispatch.
